Unit tests

### 2018-03-08 Tests.Rmd
moved some testing from copsurrog2d.R to Tests.Rmd and made better comments for the new context. Have not run it yet.

@@

>>>>

# Test skewness and third central moment functions

```{r}
source("SkewnessAnd3CentMom.R")
#Dan fill in - see if there is testing text in the file itself 
```

@@

<!--Test the copsurrog2d stat-->
```{r test_copsurrog2d, echo=T}
#Test copsurrog2d

source("copsurrog2d.R")
set.seed(101)

#***basic tests of the function using kendall-preserving surrogates
datcop<-claytonCopula(5,2)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p')

tarcop<-gumbelCopula(3,2)

res<-copsurrog2d(m,tarcop,'kendall',3)
dim(res) 
if (sum(dim(res)==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

cor(m[,1],m[,2],method='kendall') #this should be similar to the following 
cor(res[,1,1],res[,2,1],method='kendall')
cor(res[,1,2],res[,2,2],method='kendall')
cor(res[,1,3],res[,2,3],method='kendall')

plot(res[,1,1],res[,2,1],type='p') #should look like a Gumbel
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

if (sum(sort(res[,1,1])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,1])==sort(m[,2]))==numpts &&
    sum(sort(res[,1,2])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,2])==sort(m[,2]))==numpts &&
    sum(sort(res[,1,3])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,3])==sort(m[,2]))==numpts)
{
  print("passed")
} else
{
  print("Columns of output of copsurrog should be permutations of the corresponding columns of the input")
}

#basic tests using spearman preserving surrogates
res<-copsurrog2d(m,tarcop,'spearman',3)
dim(res)
if (sum(dim(res)==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

cor(m[,1],m[,2],method='spearman') #this should be similar to the following 
cor(res[,1,1],res[,2,1],method='spearman')
cor(res[,1,2],res[,2,2],method='spearman')
cor(res[,1,3],res[,2,3],method='spearman')

plot(res[,1,1],res[,2,1],type='p') #should look like a Gumbel
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

if (sum(sort(res[,1,1])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,1])==sort(m[,2]))==numpts &&
    sum(sort(res[,1,2])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,2])==sort(m[,2]))==numpts &&
    sum(sort(res[,1,3])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,3])==sort(m[,2]))==numpts)
{
  print("passed")
} else
{
  print("Columns of output of copsurrog should be permutations of the corresponding columns of the input")
}
```

<!--test to see whether changing the copula
markedly influences the distribution
of the spatial mean-->
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
#***test to see whether changing the copula
#markedly influences the distribution
#of the spatial mean
set.seed(101)

#make the data
datcop<-rotCopula(claytonCopula(5,2))
d<-rCopula(10000,datcop)
d<-qnorm(d,mean=0,sd=1)

#change the copula
tarcop<-claytonCopula(3,2)
sur<-copsurrog2d(d,tarcop,"kendall",1000)

#see how the skewness of the spatial average
#is affected
source("SkewnessAnd3CentMom.R")
skdat<-myskns(apply(FUN=mean,X=d,MARGIN=1)) #skewness of spatial mean of data
mnres<-apply(FUN=mean,X=sur,MARGIN=c(1,3)) 
sksur<-apply(FUN=myskns,X=mnres,MARGIN=2) #skewnesses of spatial means of surrogate datasets
sum(sksur<skdat)/length(sksur) #skewnesses of surrogs should be less than that of data
range(sksur) #these should mostly be negative
skdat #this should be positive

#now do the same thing but preserve the spearman instead
sur<-copsurrog2d(d,tarcop,"spearman",1000)
skdat<-myskns(apply(FUN=mean,X=d,MARGIN=1))
mnres<-apply(FUN=mean,X=sur,MARGIN=c(1,3))
sksur<-apply(FUN=myskns,X=mnres,MARGIN=2)
sum(sksur<skdat)/length(sksur) #skewnesses of surrogs should be less than that of data
range(sksur) #these should mostly be negative
```
